Designing Qusecs Optimally: Quasi-uniform or Self-similar Layered Materials as Recursively Decomposed Solutions of Geometric Constraint Systems

### 2014-12-16 doc/GMP2015/s03_drp.tex

\section{The Canonical Decomposition-Recombination Plan}

@@

\begin{theorem}\label{t1}
Given a well-constrained 2-dimensional bar-joint graph $G$, for node $C$ in $OptimalDRP(G)$ and the children of $C$ in $CompleteDRP(C)$ labeled as $C_1,\ldots,C_N$
\begin{enumerate}
    \item if $C_i \cap C_j$ is trivial then all $C_1,\ldots,C_N$ are children of $C$ in $OptimalDRP(G)$
    \item if $C_i \cap C_j$ is well-constrained then any two out of $C_1,\ldots,C_N$ will be the only children of $C$ in $OptimalDRP(G)$.
\end{enumerate}
\end{theorem}

% We develop this notion of the canonical optimal DR-plan by carefully considering the case of a union of any two non-trivial well-constrained vertex-maximal proper subgraphs of a well-constrained graph. By definition, any subgraph of a well-constrained graph will either be (1) trivial, (2) under-constrained, or (3) well-constrained. We will analyze all 3 possibilities in turn. These observations will lead to interesting properties that govern the behavior of optimal DR-plans on well-constrained graphs.

% We show this by carefully considering all of the potential cases of the unions of subgraphs. By definition, any subgraph of a well-constrained graph will either be (1) under-constrained, (2) well-constrained, or (3) trivial. We will analyze all 3 possibilities in turn, in the case of a union of any two non-trivial well-constrained vertex-maximal proper subgraphs.

@@

\subsubsection{Relationships for the Union and Intersection of Well-Constrained Subgraphs}
For the following lemmas, we define $F_i$ and $F_j$ as well-constrained subgraphs of the same well-constrained graph $F$.
We wish to prove the following bijections:

\begin{center}
\begin{tabular}{|c|c|}
\hline
\textbf{Union is\ldots} & \textbf{Intersection is\ldots} \\ \hline
\sout{trivial}          & --- \\ \hline
under-constrained       & trivial \\ \hline
well-constrained        & well-constrained \\ \hline
---                     & \sout{under-constrained} \\ \hline
\end{tabular}
\end{center}

\begin{lemma}\label{t-l1}
$F_i\cup F_j$ cannot be trivial.
\end{lemma}

\begin{proof}
% If $F_i,F_j$ are well-constrained, then $F_i\cup F_j \geq k$. Trivial graphs must be over-constrained.

Follows from the definition of a trivial graph. It would imply that the well-constrained graphs were also trivial since they would be subgraphs of a trivial graph.
\end{proof}

\begin{lemma}\label{uc-l1}
$F_i\cup F_j$ is under-constrained if and only if $F_i\cap F_j$ is trivial.
\end{lemma}

\begin{proof}
It follows from definitions that $d(F_i)=k$ and $d(F_j)=k$. In the forward direction, we have that $d(F_i\cup F_j)=l<k$. If it were equal to $k$ it would be well-constrained since, as a subgraph of $F$, it satisfies the other properties of a well-constrained graph; if it were greater than $k$ then it would be over-constrained. Therefore $d(F_i\cap F_j)=d(F_i)+d(F_j)-d(F_i\cup F_j)=2k-l>k$. The only way to have an over-constrained subgraph in a well-constrained graph is if it is trivial.

In the reverse direction, we know that $d(F_i\cap F_j)>k$ because it is trivial. Thus, by the same math, it is clear that $d(F_i\cup F_j)<k$ and it must be under-constrained.
\end{proof}

\begin{lemma}\label{wc-l1}
$F_i\cup F_j$ is well-constrained if and only if $F_i\cap F_j$ is well-constrained.
\end{lemma}

\begin{proof}
It follows from definitions that $d(F_i)=k$ and $d(F_j)=k$. In the forward direction we have that $d(F_i\cup F_j)=k$, therefore $d(F_i\cap F_j)=d(F_i)+d(F_j)-d(F_i\cup F_j)=k$. Since $F_i\cap F_j$ is a subgraph of $F$, which is well-constrained, it is also well-constrained.

In the reverse direction the same math proves that $d(F_i\cup F_j)=k$ and, since it is also a subgraph of $F$, it too is well-constrained.

% \todo{Integrate this}
% Furthermore, all subgraphs of $F_i\cup F_j$ and $F_i\cap F_j$ are also subgraphs of $F_i$ and $F_j$, therefore all properties of well-constrained graphs are maintained.

% In the forward direction: From Lemma \ref{uc-l1}, the intersection cannot be trivial. The intersection also cannot be under-constrained. If $F_i \cap F_j$ were under-constrained, then for $F_i$ to be well-constrained you would need to add more constraints (edge weight) than degrees of freedom (vertex weight) to the intersection. The same is true for $F_j$. If both of these were satisfied, then the union of $F_i$ and $F_j$ would result in an over-constrained non-trivial graph. This is a contradiction, by definition of a well-constrained graph. Therefore, the intersection can only be well-constrained.

% reverse!!!!!
\end{proof}

\begin{lemma}\label{iuc-l1}
$F_i\cap F_j$ cannot be under-constrained.
\end{lemma}

\begin{proof}
Subgraphs of well-constrained graph $F$ can only be trivial, under-constrained, or well-constrained. So it follows from Lemmas \ref{t-l1}, \ref{uc-l1}, and \ref{wc-l1} that only trivial and well-constrained intersections are possible.
\end{proof}

% WAIT... WHAT ABOUT TWO BANANAS? The intersection is 2 vertices which is under-constrained... oh nevermind... that's well-constrained

@@

\subsubsection{Inferring Parent Structure from Union and Intersection of Children}

\begin{lemma}\label{wc-l2}
% Given a well-constrained $G$ and two well-constrained vertex-maximal proper subgraphs $C_i, C_j$,
$C_i\cup C_j$ is well-constrained if and only if $C_i\cup C_j = C$.
\end{lemma}

\begin{proof}
The forwards direction can be shown with a contradiction. If the $C_i\cup C_j$ was well-constrained but $C_i\cup C_j \neq C$, we would have found a larger well-constrained proper subgraph containing them; namely, $C_i\cup C_j$ or something containing it would have been larger. The two original subgraphs could not have been vertex-maximal proper.

The reverse direction follows from the fact that $C$ is either some non-leaf node (well-constrained by definition of a DR-plan) or $G$ itself (well-constrained by definition of the problem).
\end{proof}

\begin{corollary}\label{wc-c1}
% Given a well-constrained $G$ and two well-constrained vertex-maximal proper subgraphs $C_i, C_j$, l
Let us say $R_i=C\setminus C_i$ and $R_j=C\setminus C_j$. If $C_i\cup C_j$ is well-constrained, then there can be no edges in $C$ between the vertices of $R_i$ and $R_j$.
\end{corollary}

\begin{proof}
It follows from the fact that $C_i\cup C_j$ must equal $C$ (proven in Lemma \ref{wc-l2}).
\end{proof}

At this point we limit our discussion to the scope of 2D graphs. All vertex weights are $2$, all edge weights are $1$, and constant $k= -{{3}\choose{2}}=-3$. Trivial graphs are a single vertex and empty set.

Also, 2D well-constrained graphs must be connected.
% \todo{Is this actually true?}
The greatest density of a 2D well-constrained graph is $-2$ (the vertex). The other disconnected part of the graph would need to have a density of $-1$, which is over-constrained and not possible in a well-constrained graph (because there is no trivial graph with that density).

\begin{lemma}\label{wc-l3}
If $C_i\cup C_j=C$, then $\forall k: C_i\cup C_k=C$.
Alternatively, if $C_i\cup C_j$ is well-constrained, then $\forall k: C_i\cup C_k$ is well-constrained.
\end{lemma}

\begin{proof}
Let us say $R_i=C\setminus C_i$, $R_j=C\setminus C_j$, and $D_{i,j}=C_i\cap C_j=(C\setminus R_i)\setminus R_j$ (note that $R_j\subset C_i$, $R_i\subset C_j$ and $D_{i,j}\subset C_i,C_j$). Furthermore, we have the proper subgraphs $R'_i\subset R_i$, $R'_j\subset R_j$, and $D'_{i,j}\subset D_{i,j}$ which are not empty sets.

Then we assume that there is some third well-constrained vertex-maximal proper subgraph $C_k$ (with $C'_k=C\setminus C_k$). There are $3\times 3\times 3 = 27$ possible cases for what this subgraph could be.

\begin{itemize}
    \item 3 cases: $C_k$ cannot be $C=Idc(C,R_i\cup R_j\cup D_{i,j})$, $C_i=Idc(C,R_j\cup D_{i,j})$, or $C_j=Idc(C,R_i\cup D_{i,j})$. This is by definition.

    \item 13 cases: $C_k$ cannot be a proper subgraph of $C_i$ and $C_j$ or else $C_k$ would not be vertex-maximal. These are the graphs $Idc(C,R'_i\cup D_{i,j})$, $Idc(C,R'_j\cup D_{i,j})$, $Idc(C, D_{i,j})$, $Idc(C,R_i\cup D'_{i,j})$, $Idc(C,R_j\cup D'_{i,j})$, $Idc(C,R'_i\cup D'_{i,j})$, $Idc(C,R'_j\cup D'_{i,j})$, $Idc(C, D'_{i,j})$, $Idc(C,R_i)$, $Idc(C,R_j)$, $Idc(C,R'_i)$, $Idc(C,R'_j)$, and $Idc(C,\emptyset)$.

    \item 2 cases: $C_k$ cannot contain $C_i$ or $C_j$ as proper subgraphs, or else they were not vertex-maximal. These are the graphs $Idc(C,R'_i\cup R_j\cup D_{i,j})$ and $Idc(C,R_i\cup R'_j\cup D_{i,j})$ respectively.

    \item 4 cases: \todo{Uses 2D requirement:} $C_k$ cannot be $Idc(C,R_i\cup R_j)$, $Idc(C,R'_i\cup R_j)$, $Idc(C,R_i\cup R'_j)$, or $Idc(C,R'_i\cup R'_j)$ because these are all disconnected (Corollary \ref{wc-c1}) and cannot be well-constrained.

    \item 1 case: $C_k=Idc(C,R'_i\cup R'_j\cup D_{i,j})$ is not possible. Since $C_k\cup C_i = Idc(C,R'_i\cup R_j\cup D_{i,j})\neq C$ we have from Lemma \ref{wc-l2} that $C_k\cup C_i$ cannot be well-constrained. We also know it cannot be trivial because it contains well-constrained subgraphs. This means it must be under-constrained. From Lemma \ref{uc-l1}, we know that $C_k\cap C_i=Idc(C,R'_j\cup D_{i,j})$ must then be trivial. This is impossible because $D_{i,j}$ is well-constrained, thereby contradicting the assumption that $C_k$ is well-constrained.

    \item 1 case: \todo{Uses 2D requirement:} $C_k=Idc(C,R'_i\cup R'_j\cup D'_{i,j})$ is not possible. The union with $C_i$ (or $C_j$) is not equal to $C$. Therefore, the union must be under-constrained which means the intersection must be trivial (a single node). However, $C_k\cap C_i=Idc(C,R'_j\cup D'_{i,j})$ and since $R'_j$ and $D'_{i,j}$ are not empty sets, it cannot be trivial making a contradiction.

    \item 2 cases: \todo{Uses 2D requirement:} $C_k=Idc(C,R'_i\cup R_j\cup D'_{i,j})$ and $C_k=Idc(C,R_i\cup R'_j\cup D'_{i,j})$ are not possible. The proof mirrors the previous case, except here you must choose $C_i$ and $C_j$ respectively.

    \item 1 case: $C_k=Idc(C,R_i\cup R_j\cup D'_{i,j})$ is all that remains.
\end{itemize}

Since $D_{i,j}\subset C_i, C_j$ it means that $C_k\cup C_i = C_k \cup C_j = C$, thus proving the Lemma.

\todo{Needs a figure.}
\end{proof}

% \pnplaceholder
% WAIT, TRIVIAL GRAPH DEFINITION DOESN'T WORK!!!! in 4D it's the 3 clique, but 3 vertices is a subgraph of that... that is certainly not over-constrained...

% NOT SO! -5C2 = -10. 3 edges and 3 nodes -> 3 - 3*4 = -9... over-constrained!

% \pnplaceholder

\begin{lemma}\label{uc-l2}
% If there exist $C_i, C_j$ such that $C_i\cap C_j$ is trivial, then for all $C_k,C_l$, $C_k\cap C_l$ is trivial (a vertex or empty set).
If $C_i\cap C_j$ is trivial, then $\forall k: C_i\cap C_k$ is trivial.
\end{lemma}

\begin{proof}
If some $C_i\cap C_k$ is not trivial, then it must be well-constrained. Then, by Lemma \ref{wc-l3}, all of the intersections are well-constrained. This contradicts the statement that $C_i\cap C_j$ is trivial.
% It follows that if the intersection is trivial then the union is under-constrained (Lemma \ref{uc-l1}). If the union is under-constrained, then the
\end{proof}

@@

\subsubsection{Proving the Main Theorem \ref{t1}}\label{sec:maintheorem}
Lemmas \ref{wc-l3} and \ref{uc-l2} show that $CompleteDRP(C)$ will result in one of two scenarios. (A) Either all $C_1,\ldots,C_N$ intersect on some common well-constrained subgraph and any two union to make $C$, or (B) all $C_1,\ldots,C_N$ intersect trivially and all of them must be unioned to make $C$.

% \begin{theorem}
% In case (A), any two unique wcvmps of $C$ can be used as the children of $C$ in $OptimalDRP(C)$.
% \end{theorem}

% \begin{proof}

% \end{proof}

% \begin{theorem}
% In case (B), all wcvmps of $C$ must be used as the children of $C$ in $OptimalDRP(C)$.
% \end{theorem}

% \begin{proof}
% If not all of them are used, the union will be under-constrained. $C$ is well-constrained, thus using not all of them is not an option.
% \end{proof}

% \pnplaceholder

% \pagebreak
% See ISSUE at top of paper, we have to assume we have a connected $G$...

% Take $C'_i$ to be $C\setminus C_i$. Then if $C_i\cup C_j$ is well-constrained we have directly from Lemma \ref{wc-l2} for all $C'_i, C'_j$ there can be no edges between them (otherwise $C_i\cup C_j\neq C$).

% The set of edges connecting $C'_i$ to $C_i$ must have a weight that sums to exactly $d(C'_i)$ since we know that $d(C)=d(C_i)=k$.

% Any other $C_k$ must therefore contain $C'_i$ and $C'_j$ because it adds no density to ``tack it on'' to a graph that does not contain them already.

% Now we want to know something about $C_k$. If $C_k \neq C_i$, then $C'_i\not\subseteq C'_k$. It is clear that they cannot be equal otherwise $C_k = C_i$. However, it also cannot be a subset. There are two scenarios. (1) $C'_k$ does not contain vertices that are incident to $C'_i$. If this were so, we know we could ``tack on'' $C'_i$ to the well-constrained $C_k$ without increasing the density and therefore $C_k$ could not have been maximal in the first place. (2) $C'_k$ contains vertices that are incident to $C'_i$. In this case

% Take $D_{i,j}$ to be $C\setminus (C'_i\cup C'_j)$. Clearly $D_{i,j}$ must be well-constrained since ``tacking on'' $C'_i$ and $C'_j$ adds no density and $C$ is well-constrained. Therefore, if there were some other $C_k$, it must contain $D_{i,j,k}\subset D_{i,j}$ such that $D_{i,j,k}=D_{i,j}\setminus C'_k$. It is clear that $D_{i,j,k}$ cannot equal $D_{i,j}$ or else $C_k$ must be $C_i$ or $C_j$ to be vertex-maximal.

% \begin{lemma}
% If there exist $C_i, C_j$ such that $C_i\cap C_j$ is trivial, then for all $C_k,C_l$, $C_k\cap C_l$ is trivial or empty set.
% \end{lemma}

% \begin{proof}
% By Lemmas... the union must be under
% Lemma \ref{uc-l1} that $C_i\cup C_j$ must be under-constrained. Therefore, by the proof
% It follows from Lemma \ref{wc-l1} that the only way to get
%  and its proof that if any intersections
% \end{proof}

@@

\begin{theorem}\label{wc-t1}
% In $OptimalDRP(G)$ of a well-constrained $G$, if any two well-constrained vertex-maximal proper subgraphs of a node form a union that is well-constrained, then said node can have only $2$ children.

In $OptimalDRP(G)$ of a well-constrained $G$, if $C_i \cup C_j$ is well-constrained, then any 2 well-constrained vertex-maximal proper subgraphs of $C$ will be sufficient as its children.
% Namely, these children are any 2 of its well-constrained vertex-maximal proper subgraphs.
\end{theorem}

\begin{proof}
In a valid DR-plan, all children must be proper subgraphs. Therefore, for the union to be the parent (and satisfy the conditions of a DR-plan) there must be at least two children. It follows directly from Lemma \ref{wc-l3} that if there exists $C_i, C_j$ such that $C_i \cup C_j$ is well-constrained, then the smallest fan-in at this node can be made by selecting any two $C_i, C_j$.
% you found a tree with only 2 children.
% Clearly, this is the optimal choice at this level.
However, for it to be a solution to $OptimalDRP(G)$, it must not affect the maximum fan-in for any descendant.

Take $D=\bigcap_{k=1}^N{C_k}$ and $R_k=C\setminus C_k$.
% This means that $D$ is also $\bigcup_{k=1}^N{R_k}$.
Suppose we select $i$ and $j$, where $i\neq j$, as the children. Since
% \[C_i=Idc\left(C,D\cup\bigcup_{k\in N\setminus\{i\}}{R_k}\right)\]
% the children of this node will be
% \[Idc\left(C,D\cup\bigcup_{k\in N\setminus\{i,m\}}{R_k}\right)\]
% and
% \[Idc\left(C,D\cup\bigcup_{k\in N\setminus\{i,n\}}{R_k}\right)\]
$C_i=Idc\left(C,D\cup\bigcup_{k\in N\setminus\{i\}}{R_k}\right)$
the children of this node will be
$Idc\left(C,D\cup\bigcup_{k\in N\setminus\{i,m\}}{R_k}\right)$
and
$Idc\left(C,D\cup\bigcup_{k\in N\setminus\{i,n\}}{R_k}\right)$
for arbitrary $m$ and $n$, where $m\neq n$. This continues for $N-1$ levels total, always with fan-in of two, at which point every descendant of $C$ is some $Idc(C,D\cup R_k)$.

% This is demonstrated with $N=3$ in Figure \ref{3-plans}. It is clear that until this point, the fan-in at every node is exactly 2 in the optimal solution. This follows from the discussion above. Now, at this level, the fan-in must be equal in all scenarios. In fact, at node $k$ it will be 1 (because of $D$ which is well-constrained) plus whatever fan-in $R_k$ incurs.
\end{proof}

\begin{theorem}\label{uc-t1}
% In any solution to $OptimalDRP(G)$, if any two well-constrained vertex-maximal proper subgraphs of a node form a union that is under-constrained, then all well-constrained vertex-maximal proper subgraphs of said node must be included in the optimal plan.

In $OptimalDRP(G)$ of a well-constrained $G$, if $C_i \cap C_j$ is trivial, then all $C_1,\ldots, C_N$ must be included in the optimal plan as children of $C$.
\end{theorem}

@@

\todo{Uses 2D requirement:}
If $D= C$, then we contradict the assumption that $C_i \cap C_j$ is trivial. By Lemma \ref{uc-l2}, if $C_i \cap C_j$ is trivial then for $k\notin X$, $D\cap C_k$ must be one or more trivial subgraphs. Furthermore, by definition of a DR-plan, $C_k=C\cap C_k=D\cap C_k$. Together, this shows that $C_k$ cannot be well-constrained, violating the properties of a DR-plan.
\end{proof}

@@

With these two proofs, the original Theorem \ref{t1} has been proven. With this we have formulated the notion of a canonical DR-plan.
% Any optimal DR-plan of a well-constrained graph must follow this pattern.
No matter which two children you choose in case (A) the recombination steps will always involve the same systems; in case (B), all children must always be included.

% (2) If the union results in a well-constrained subgraph, it must be the entire graph. If this were not the case, .

% More can be said about the intersection of these two subgraphs, $C_1=(V_1, E_1)$ and $C_2=(V_2, E_2)$. It cannot be over-constrained, otherwise the union could not be well-constrained (simple arithmetic, see the first case).

@@

% \subsection{Further Results}

@@

% \begin{proof}
% Explained in Theorem \ref{wc-t1}.
% \end{proof}

@@

% \begin{proof}
% Further constraints between them would imply $C_i \cup C_j$ is a subgraph of $C$, but lemma \ref{wc-l2} proves is the entire graph.
% \end{proof}

% \begin{proof}
% It follows from Theorem \ref{uc-t1} that if the intersection of any two well-constrained vertex-maximal proper subgraphs of $C$ are well-constrained then all of them are well-constrained or $\emptyset$.
% \end{proof}

@@

\begin{example}
    In figure \ref{doublets}, the two well-constrained vertex-maximal proper subgraphs of the graph are the two doublets, shown in the second level of the DR-plan. These intersect on the well-constrained graph $\{b_1,b_2,b_3\}$. This will necessarily be a child $N=2$ levels below the parent of the two doublets, as explained in Theorem \ref{wc-t1}. Also shown is the decomposition of the individual doublets. These have five well-constrained vertex-maximal proper subgraphs, the two triangles and the three edges connecting them. As explained in Theorem \ref{uc-t1}, all of them must be included in the optimal DR-plan. Were any left out, the union of the children would not be the entire parent.
\end{example}

>>>>

\section{The Canonical Decomposition-Recombination Plan}
\label{sec:DRP}

@@

\begin{theorem}\label{theorem:main}
Given a well-constrained 2-dimensional bar-joint graph $G$, for node $C$ in $OptimalDRP(G)$ and the children of $C$ in $CompleteDRP(C)$ labeled as $C_1,\ldots,C_N$
\begin{enumerate}
    \item if $C_i \cap C_j$ is trivial then all $C_1,\ldots,C_N$ are children of $C$ in $OptimalDRP(G)$
    \item if $C_i \cap C_j$ is well-constrained then any two out of $C_1,\ldots,C_N$ will be the only children of $C$ in $OptimalDRP(G)$.
\end{enumerate}
\end{theorem}

% \begin{proof}
% Immediate from Lemma \ref{lemma:main_trivial} and \ref{lemma:main_wellconstrained}.
% \end{proof}

% \begin{lemma}\label{lemma:main_trivial}
% In $OptimalDRP(G)$ of a well-constrained $G$, if $C_i \cap C_j$ is trivial, then all $C_1,\ldots, C_N$ must be included in the optimal plan as children of $C$.
% \end{lemma}

% \begin{lemma}\label{lemma:main_wellconstrained}
% In $OptimalDRP(G)$ of a well-constrained $G$, if $C_i \cup C_j$ is well-constrained, then any 2 well-constrained vertex-maximal proper subgraphs of $C$ will be sufficient as its children.
% \end{lemma}

@@

\subsubsection{Relationships for the Union and Intersection of Well-Constrained Subgraphs}
\label{sec:union_intersection}

\begin{lemma}\label{lemma:union_intersection}
If $F_i$ and $F_j$ are well-constrained subgraphs of the same well-constrained graph $F$, then it must be that:
\begin{enumerate}
    \item $F_i\cup F_j$ is not trivial.
    \item $F_i\cup F_j$ is under-constrained if and only if $F_i\cap F_j$ is trivial.
    \item $F_i\cup F_j$ is well-constrained if and only if $F_i\cap F_j$ is well-constrained.
    \item $F_i\cap F_j$ is not under-constrained.
\end{enumerate}
\end{lemma}

\begin{proof}
Note that, by definition, $d(F_i)=k$ and $d(F_j)=k$. Also, $d(F_i\cap F_j)=d(F_i)+d(F_j)-d(F_i\cup F_j)$.
\begin{enumerate}
    \item By definition of trivial graph; if $F_i\cup F_j$ were trivial, then $F_i$ and $F_j$ must be trivial.

    \item \textit{Forward direction:} Since $F_i\cup F_j$ is under-constrained and a subgraph of well-constrained $F$, it must be that $d(F_i\cup F_j)=l<k$. Therefore $d(F_i\cap F_j)=2k-l>k$. This means $F_i\cap F_j$ is trivial. \textit{Reverse direction:} We know that $d(F_i\cap F_j)>k$ because it is trivial. By the same math, we find that $d(F_i\cup F_j)<k$, showing it is under-constrained.

    \item \textit{Forward direction:} We have that $d(F_i\cup F_j)=k$, therefore $d(F_i\cap F_j)=k$. Being a subgraph of well-constrained $F$, $F_i\cap F_j$ is also well-constrained. \textit{Reverse direction:} By the same math, we find that $d(F_i\cup F_j)=k$ and, since it is also a subgraph of $F$, it is well-constrained.

    \item Subgraphs of well-constrained graph $F$ can only be trivial, under-constrained, or well-constrained. So it follows from the above that an under-constrained intersection is not possible.
\end{enumerate}
\end{proof}

% For the following lemmas, we define $F_i$ and $F_j$ as well-constrained subgraphs of the same well-constrained graph $F$.
% We wish to prove the following bijections:

% \begin{center}
% \begin{tabular}{|c|c|}
% \hline
% \textbf{Union is\ldots} & \textbf{Intersection is\ldots} \\ \hline
% \sout{trivial}          & --- \\ \hline
% under-constrained       & trivial \\ \hline
% well-constrained        & well-constrained \\ \hline
% ---                     & \sout{under-constrained} \\ \hline
% \end{tabular}
% \end{center}

% \begin{lemma}\label{t-l1}
% $F_i\cup F_j$ cannot be trivial.
% \end{lemma}

% \begin{proof}
% Follows from the definition of a trivial graph. It would imply that the well-constrained graphs were also trivial since they would be subgraphs of a trivial graph.
% \end{proof}

% \begin{lemma}\label{uc-l1}
% $F_i\cup F_j$ is under-constrained if and only if $F_i\cap F_j$ is trivial.
% \end{lemma}

% \begin{proof}
% It follows from definitions that $d(F_i)=k$ and $d(F_j)=k$. In the forward direction, we have that $d(F_i\cup F_j)=l<k$. If it were equal to $k$ it would be well-constrained since, as a subgraph of $F$, it satisfies the other properties of a well-constrained graph; if it were greater than $k$ then it would be over-constrained. Therefore $d(F_i\cap F_j)=d(F_i)+d(F_j)-d(F_i\cup F_j)=2k-l>k$. The only way to have an over-constrained subgraph in a well-constrained graph is if it is trivial.

% In the reverse direction, we know that $d(F_i\cap F_j)>k$ because it is trivial. Thus, by the same math, it is clear that $d(F_i\cup F_j)<k$ and it must be under-constrained.
% \end{proof}

% \begin{lemma}\label{wc-l1}
% $F_i\cup F_j$ is well-constrained if and only if $F_i\cap F_j$ is well-constrained.
% \end{lemma}

% \begin{proof}
% It follows from definitions that $d(F_i)=k$ and $d(F_j)=k$. In the forward direction we have that $d(F_i\cup F_j)=k$, therefore $d(F_i\cap F_j)=d(F_i)+d(F_j)-d(F_i\cup F_j)=k$. Since $F_i\cap F_j$ is a subgraph of $F$, which is well-constrained, it is also well-constrained.

% In the reverse direction the same math proves that $d(F_i\cup F_j)=k$ and, since it is also a subgraph of $F$, it too is well-constrained.
% \end{proof}

% \begin{lemma}\label{iuc-l1}
% $F_i\cap F_j$ cannot be under-constrained.
% \end{lemma}

% \begin{proof}
% Subgraphs of well-constrained graph $F$ can only be trivial, under-constrained, or well-constrained. So it follows from Lemmas \ref{t-l1}, \ref{uc-l1}, and \ref{wc-l1} that only trivial and well-constrained intersections are possible.
% \end{proof}

@@

\subsubsection{Inferring Parent Structure from Union and Intersection of Children}
\label{sec:infer_parent}

\begin{lemma}\label{lemma:wc_intersection_is_C}
$C_i\cup C_j$ is well-constrained if and only if $C_i\cup C_j = C$.
\end{lemma}

\begin{proof}
\textit{Forward direction:} Proof by contradiction. If the $C_i\cup C_j$ was well-constrained but $C_i\cup C_j \neq C$, we would have found a larger well-constrained proper subgraph containing them; namely, $C_i\cup C_j$ or something containing it. The two original subgraphs could not have been vertex-maximal proper.

\textit{Reverse direction:} $C$ is either some non-leaf node (well-constrained by definition of a DR-plan) or $G$ itself (well-constrained by definition of the problem). Thus, $C_i\cup C_j$ is well-constrained.
\end{proof}

\begin{corollary}\label{corollary:no_edges_between_diff}
Let us say $R_i=C\setminus C_i$ and $R_j=C\setminus C_j$. If $C_i\cup C_j$ is well-constrained, then there can be no edges in $C$ between the vertices of $R_i$ and $R_j$.
\end{corollary}

\begin{proof}
Lemma \ref{lemma:wc_intersection_is_C} shows that $C_i\cup C_j$ must equal the entire parent $C$.
\end{proof}

At this point we limit our discussion to the scope of 2D graphs. All vertex weights are $2$, all edge weights are $1$, and constant $k= -{{3}\choose{2}}=-3$. Trivial graphs are a single vertex and empty set. Furthermore, 2D well-constrained graphs must be connected.
% The greatest density of a 2D well-constrained graph is $-2$ (the vertex). The other disconnected part of the graph would need to have a density of $-1$, which is over-constrained and not possible in a well-constrained graph (because there is no trivial graph with that density).

\begin{lemma}\label{lemma:wc_intersection_makes_all_wc}
If $C_i\cup C_j$ is well-constrained, then $\forall k: C_i\cup C_k$ is well-constrained.
Alternatively, if $C_i\cup C_j=C$, then $\forall k: C_i\cup C_k=C$.
\end{lemma}

\begin{proof}
In appendix (\ref{sec:appendix}).
\end{proof}

\begin{lemma}\label{lemma:uc_intersection_makes_all_uc}
If $C_i\cap C_j$ is trivial, then $\forall k: C_i\cap C_k$ is trivial.
\end{lemma}

\begin{proof}
By Lemma \ref{lemma:union_intersection}, if some $C_i\cap C_k$ is not trivial, then it must be well-constrained. Then, by Lemma \ref{lemma:wc_intersection_makes_all_wc}, all of the intersections are well-constrained. This contradicts the statement that $C_i\cap C_j$ is trivial.
\end{proof}

@@

\subsubsection{Proving the Main Theorem \ref{theorem:main}}
\label{sec:maintheorem}
Lemmas \ref{lemma:wc_intersection_makes_all_wc} and \ref{lemma:uc_intersection_makes_all_uc} show that $CompleteDRP(C)$ will result in one of two scenarios. (A) Either all $C_1,\ldots,C_N$ intersect trivially and all of them must be unioned to make $C$, or (B) all $C_1,\ldots,C_N$ intersect on some common well-constrained subgraph and any two union to make $C$.

@@

\begin{theorem}\label{theorem:main_wellconstrained}
In $OptimalDRP(G)$ of a well-constrained $G$, if $C_i \cap C_j$ is trivial, then all $C_1,\ldots, C_N$ must be included in the optimal plan as children of $C$.
\end{theorem}

@@

\todo{Uses 2D requirement:}
If $D= C$, then we contradict the assumption that $C_i \cap C_j$ is trivial. By Lemma \ref{lemma:uc_intersection_makes_all_uc}, if $C_i \cap C_j$ is trivial then for $k\notin X$, $D\cap C_k$ must be one or more trivial subgraphs. Furthermore, by definition of a DR-plan, $C_k=C\cap C_k=D\cap C_k$. Together, this shows that $C_k$ cannot be well-constrained, violating the properties of a DR-plan.
\end{proof}

@@

\begin{theorem}\label{theorem:main_trivial}
In $OptimalDRP(G)$ of a well-constrained $G$, if $C_i \cup C_j$ is well-constrained, then any 2 well-constrained vertex-maximal proper subgraphs of $C$ will be sufficient as its children.
% Namely, these children are any 2 of its well-constrained vertex-maximal proper subgraphs.
\end{theorem}

\begin{proof}
In a valid DR-plan, all children must be proper subgraphs. Therefore, for the union to be the parent (and satisfy the conditions of a DR-plan) there must be at least two children. It follows directly from Lemma \ref{lemma:wc_intersection_makes_all_wc} that if there exists $C_i, C_j$ such that $C_i \cup C_j$ is well-constrained, then the smallest fan-in at this node can be made by selecting any two $C_i, C_j$.
% you found a tree with only 2 children.
% Clearly, this is the optimal choice at this level.
However, for it to be a solution to $OptimalDRP(G)$, it must not affect the maximum fan-in for any descendant.

Take $D=\bigcap_{k=1}^N{C_k}$ and $R_k=C\setminus C_k$. Suppose we select $i$ and $j$, where $i\neq j$, as the children. Since
% \[C_i=Idc\left(C,D\cup\bigcup_{k\in N\setminus\{i\}}{R_k}\right)\]
% the children of this node will be
% \[Idc\left(C,D\cup\bigcup_{k\in N\setminus\{i,m\}}{R_k}\right)\]
% and
% \[Idc\left(C,D\cup\bigcup_{k\in N\setminus\{i,n\}}{R_k}\right)\]
$C_i=Idc\left(C,D\cup\bigcup_{k\in N\setminus\{i\}}{R_k}\right)$
the children of this node will be
$Idc\left(C,D\cup\bigcup_{k\in N\setminus\{i,m\}}{R_k}\right)$
and
$Idc\left(C,D\cup\bigcup_{k\in N\setminus\{i,n\}}{R_k}\right)$
for arbitrary $m$ and $n$, where $m\neq n$. This continues for $N-1$ levels total, always with fan-in of two, at which point every descendant of $C$ is some $Idc(C,D\cup R_k)$.
\end{proof}

% This is demonstrated with $N=3$ in Figure \ref{3-plans}. It is clear that until this point, the fan-in at every node is exactly 2 in the optimal solution. This follows from the discussion above. Now, at this level, the fan-in must be equal in all scenarios. In fact, at node $k$ it will be 1 (because of $D$ which is well-constrained) plus whatever fan-in $R_k$ incurs.

With these two proofs, the original Theorem \ref{theorem:main} has been proven. With this we have formulated the notion of a canonical DR-plan.
% Any optimal DR-plan of a well-constrained graph must follow this pattern.
No matter which two children you choose in case (A) all children must always be included; in case (B), the recombination steps will always involve the same systems.

@@

% \subsubsection{Further Results}

@@

% \begin{proof}
% Explained in Theorem \ref{theorem:main_wellconstrained}.
% \end{proof}

@@

% \begin{proof}
% Further constraints between them would imply $C_i \cup C_j$ is a subgraph of $C$, but lemma \ref{lemma:wc_intersection_is_C} proves is the entire graph.
% \end{proof}

% \begin{proof}
% It follows from Theorem \ref{theorem:main_trivial} that if the intersection of any two well-constrained vertex-maximal proper subgraphs of $C$ are well-constrained then all of them are well-constrained or $\emptyset$.
% \end{proof}

@@

\begin{example}
    In figure \ref{doublets}, the two well-constrained vertex-maximal proper subgraphs of the graph are the two doublets, shown in the second level of the DR-plan. These intersect on the well-constrained graph $\{b_1,b_2,b_3\}$. This will necessarily be a child $N=2$ levels below the parent of the two doublets, as explained in Theorem \ref{theorem:main_wellconstrained}. Also shown is the decomposition of the individual doublets. These have five well-constrained vertex-maximal proper subgraphs, the two triangles and the three edges connecting them. As explained in Theorem \ref{theorem:main_trivial}, all of them must be included in the optimal DR-plan. Were any left out, the union of the children would not be the entire parent.
\end{example}
